Global case

### 2025-05-07 lipschitz/Lipitschz.tex
update

	This model

	\subsection{Simplified models}

>>>>

	This large model contains twice as many binary variables as $\mathcal{M}$. The computational cost of solving an MILP model is known to grow roughly exponentially with the number of binary variables, hence it will cost much more time.

	Therefore we need to relax more binary variables to continue variables, and/or simplify the model.

	\subsection{Simplified model}

	The first simplified model (perhaps not a simplified one), is to use one variable to the difference of each two variables, which we use $\gamma_i$ to  denote it: that is, if $x_i$ and $x'_i$ are two variables in $\mathcal{M}$ and $\mathcal{M}'$ representing the same node, then $\gamma_i=x_i-x'_i$.

	Now the constraints for $\gamma$ variables between pre-activation and post-activation is as follows:
